
\chapter*{Acknowledgments}

This project was able to be completed due to the support and guidance of many wonderful individuals in my life. I would like to first thank Professor Stuart Shieber for serving as my thesis adviser. I would not have able to complete this ambitious project without your support and guidance. My research advisor, Dr. Sylvain Jaume, helped edit my thesis and provided guidance in navigating the degree program. 

Additionally, I would like to thank my supervisors Byron Galbraith, Paula Long, as well as the Talla organization for their patience and support as I undertook this project. I was a full-time employee for Talla while working writing and researching this thesis. Balancing the demands of work while researching was challenging. I am incredibly fortunate to work for an organization that provided me with the flexibility to take time off and prioritize the completion of my degree and this thesis. Without that support, this project could not have been completed.

The idea for this project initially arose from my time at the Allen Institute for Artificial Intelligence (AI2). Vu Ha, Amos Ng and I were part of a team that was exploring novel research areas in the dialog space. This project was initially slated to be AI2's fifth research track but was quickly decommissioned after AI2 chose to prioritize other research. I greatly appreciate the blessing from Vu Ha and AI2 to be able to continue the project independently. 

This degree has taken quite a long time to complete. I started the ALM program in 2013 while working full time at Harvard. Over the course of this program, I've changed my job four times, moved across the country to Seattle and back to Cambridge. While it has been exhausting and demanding, I have had profound emotional support from my family and friends. I am grateful to mother (Shobha), father (Bharat), and sister (Dhara) for continuing to nag, push, and of course provide generous amounts of love and encouragement. I am also thankful for my dear friend and partner Camille Shaw who sent pictures of cute animals daily to motivate me and provided so much emotional support. And finally, thank you Thakurji for blessing me and providing opportunities for success.  


%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "main"
%%% End: 
