\chapter{Conclusion}
\label{chap:conclusions}

\section{ Known Limitations and Suggestions for Future Work}
\label{sec:issues} 

Overall, the framework works as intended. One key limitation was discovered during performance testing. We found that our serialization strategy causes the framework to consume memory linearly as the number of simulations increase. This occurs because the dialog manager waits until all simulations are run before dumping the generated dialog history. As a result, the in-memory json representation grows linearly with each incremental simulation run. The remedy for this is straightforward. The dialog manager can store the dialog history in a fixed size buffer that serializes to storage when it is full. 

We also saw limitations around neural mode runtime performance and general qualitative performances in the context of nlg and nlu. The focus of this project was the engineering and development of the simulation framework. Unfortunately, we did not have time to explore how to optimize neural architectures to support our use cases. This is an exciting and active area of research and offers many interesting avenues for further inquiry.

In a related vein, we were unable to support reinforcement learning and incorporate online training of the dialog agent in our framework. There is fascinating value to extend the framework to provide reward signals and support live training of the dialog agent based off of the feedback from the user simulator. 

Finally, there is an opportunity to extend Socrates Sim by adding in a visual interface. Currently, it is command line driven. The framework is developed with modularity in mind. We have abstracted the domain logic from the implementation layer. As a result, a visual front end can be developed for Socrates Sim without modifying the underlying framework.

\section{Lessons Learned}
\label{sec:lessons}

This thesis was our first foray into task completion dialog research and statistical language understanding. While we ultimately approached this domain from an engineering perspective, we did gain a better understanding of the active research challenges and model-based approaches. Our understanding of the capabilities and limitations of neural network-based approaches was likewise enriched. 

From a software engineering perspective, the greatest challenge we ran into was walking the fine line between defining rigid conventions to ensure predictable usage versus allowing for more flexibility to empower the user. Often Socrates Sim was written and rewritten to accommodate marginal edge cases because our design choices tilted too far on the flexible side. Other times, in an effort reduce  manual coding for the end user, we tilted too far in the opposite direction and defined very rigid conventions. Our end takeaway was that it often helps to take a step back and list out the various use cases. If you can make assumptions that captures 60\% to 80\% of those use cases, then developing defined conventions is very valuable. In fact, it reduces the friction and learning curve to understand and use your tools.

Additionally, this project was a great deep dive into using the Python language for a larger scale project. One of the persistent challenges with Python is due to dynamic typing. In large projects, it is hard track bugs as objects and variable are mutable and not strictly typed. The ability to explore Python 3.5's type hinting capabilities was useful and illuminating, especially since type hinting provides a way to raise the quality of your Python code base to meet software engineering best practices and norms.

\section{Summary}

In summary, we have demonstrated the design and implementation of an end-to-end dialog simulation framework that supports task-completion dialog research. In chapter 2, we detailed a modular architecture that can be re-targeted to new domains and scaled efficiently. Central to this design were four key components. The first was the speaker abstract base class, which provides a unified interface for external user simulators and dialog agents to communicate with the framework in a standardized manner. The second was the codification of the dialog domain, where dialog acts, inform and request slots and slot values, and other pertinent information to the domain is captured. The dialog domain object is made available to the dialog manager, dialog agent, and user simulator. The third important component was the standardization of ancillary communication components like the dialog action object. Specifically, we extend and formally implement as classes the user goal and user agenda described in \cite{Schatzmann2009TheHA} to support the development of a user simulator. The final component is the dialog manager, which tracks, evaluates, and serializes simulated dialogs. 

In chapter 3, we described the general process of implementing Socrates Sim. We highlighted our configuration-first philosophy, inspired by \cite{Gardner_allennlp}, which allowed for the framework to more easily generalize to new domains. Specifically, we called out the use of the simulation configuration file. The configuration file allows the researcher to integrate an external user simulator, dialog agent, and domain into the framework. We also demonstrated modularity by supporting the dynamic loading of the nlg and nlu modules.

In chapter 4 and 5 we explored in detail how Socrates Sim was adapted for the restaurant recommendation and movie booking domains. We detailed the development of dialog domain, dialog agent, and user simulators for both domains. We showed specifically how Socrates Sim was able to support new domains and nlg/nlu models with the use of configuration files and require no code update to the underlying framework and dialog manager. In doing so, we were able to demonstrate that the framework is retargetable. 
  
In chapter 6, we described how Socrates Sim was developed. We highlighted the tools, programming language, and other development specific choices made while developing Socrates Sim. In chapter 7, we provided evidence that Socrates Sim is usable and scale efficiently. Multiple performance tests were run to evaluate the runtime efficiency and memory consumption of Socrates Sim as it ran an increasing number of simulations. We used TC-Bot (\cite{li_end_to_end}) as a benchmark to evaluate performance. 

The testing confirmed that Socrates Sim scales efficiently and predictably running up to 50,000 simulations. While Socrates Sim does scale linearly as the required number of simulations increase, performance does not degrade until you exceed 100,000 simulations. The average cost of running rules-based user simulators in Socrates Sim is between .0002 to .0131 seconds. You are able to simulate 50,000 dialogs in under two minutes, which far exceeds the performance of TC-Bot. We also find there is an opportunity for improvement in improving model-based simulations in Socrates Sim. Objectively, the average cost for a model-based simulation is .6722 seconds and it takes about one hour to run 50,000 simulations. In contrast, the average cost per simulation for TC-Bot's .2168 seconds. TC-Bot is able to run 50,00 simulations in about 30 seconds. 
 
In conclusion, we have developed a framework that supports multi-domain task completion research. We have demonstrated the framework's ability to support new domains without changing the underlying code. Additionally, our performance tests reveal that Socrates Sim scales efficiently and is generally usable. Our hope is this project can provide the foundations to support end-to-end task completion research and can be extended to provide new value by the community.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "main"
%%% End: 
